Pricing Games in Heterogeneous Parallel Networks

### 2025-02-09 thesis/slides.tex
Thesis: Pres: Improvements, examples and graphs for Sensitivity Split section

\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level)}
	Tolls $t \in \R_+^{|N|}$ can be assigned to links, affecting player cost.

@@

		% Links
		\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
		\draw[->, thick] (s) to node[midway, above] {$x + 1$} (t);
		\draw[->, thick] (s) to[bend right=35] node[midway, above] {$x + 2$} (t);
	\end{tikzpicture}
\end{center}
For homogeneous players and tolls $t = \left(4, 2, 1\right)$ we get
\[x(t) = \left(0, \frac12, \frac12\right)\]
since $\forall p \in [0, 1]$ it holds $c_2(p) = c_3(p) = 7/2$ and $c_1(p) = 4$.
\end{frame}

\begin{frame}{Preliminaries | Pricing competition (2\textsuperscript{nd} level)}
	Links are owned by agents who compete for profit.
	\begin{block}{Profit}
		For given set of tolls $t \in \R_+^{|N|}$, link operator $i$ gains profit
		\[\Pi_i(t) = x_i(t) \cdot t_i\]
	\end{block}
	\begin{block}{Best response}
		For fixed tolls assignments from remaining link operators $t_{-i} = t \setminus \{t_i\}$, link operator $i$ will try and maximise their profit
		\[B_i(t_{-i}) = \argmax_{t_i \ge 0} \Pi(t_i, t_{-i})\]
	\end{block}
\end{frame}

@@

\subsection{Heterogeneous networks}

\begin{frame}{Preliminaries | Heterogeneous players}
	\begin{lemma}
		For $\Gm = (N, \ell, \alpha)$ with tolls $t$ and flow $x(t)$ the Nash equilibrium for $t$, it holds for all $i, j \in N$ with $x_i(t), x_j(t) > 0$ that
		\begin{enumerate}[(i)]
			\item $\ell_i(x_i(t)) < \ell_j(x_j(t))$ iff $t_i > t_j$
			\item $\ell_i(x_i(t)) = \ell_j(x_j(t))$ iff $t_i = t_j$
			\item $\ell_i(x_i(t)) > \ell_j(x_j(t))$ iff $t_i < t_j$
		\end{enumerate}
	\end{lemma}
	\begin{proof}
		Assume $\ell_i(x_i(t)) < \ell_j(x_j(t))$ and $t_i < t_j$ for some $i, j \in N$.
		Then for \textbf{all} players $c_i(p) < c_j(p)$ so $x_j(t) > 0$ is a contradiction.
	\end{proof}
\end{frame}

\begin{frame}{Preliminaries | Heterogeneous players}
	Latencies are viewed the same for all players.

	Toll order is the same for all players.

	Tolls define an ordering of the $N$ links where
	\begin{itemize}
		\item $t_1 \ge t_2 \ge \dots \ge t_n$
		\item $\ell_1(x_1(t)) \le \ell_2(x_2(t)) \le \dots \le \ell_n(x_n(t))$
		\item for player representatives from each link $p_1, p_2, \dots, p_n$ we also get $\alpha(p_1) \le \alpha(p_2) \le \dots \le \alpha(p_n)$
	\end{itemize}
	Ordering is unique only when the toll (and therefore also latency) inequalities are strict.
\end{frame}

%\begin{frame}{Preliminaries | Heterogeneous players}
%	\begin{example}
%		Let $([2], \ell, \alpha)$ with $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and $\alpha(p) = p + 1$.
%	\end{example}
%	$x(0) = \left(\frac23, \frac13\right), \; x(3, 2) = \left(\frac14, \frac34\right)$
%\end{frame}

@@

\begin{frame}{Sensitivity split}
	In a heterogeneous game, in practice, each flow user plays a different game.

	In example the users are organised around the one for which $c_1(p) = c_2(p)$.

	We need the notion of the money-sensitivity value for which two link costs are equal.
\end{frame}

\begin{frame}{Sensitivity split}
	\begin{definition}
		Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$ and $x(t)$ the Nash equilibrium for $t$.
		We define the \textit{money sensitivity split function} $\as^{(i, j)}: \{t \in \R_+^N|t_i \ne t_j\} \rightarrow (0, +\infty)$ as
		\[\as^{(i, j)}(t) = \frac{\ell_j(x_j(t)) - \ell_i(x_i(t))}{t_i - t_j}\]
	\end{definition}
	If $t_i = t_j \Leftrightarrow \ell_i(x_i) = \ell_j(x_j)$ then $c_i(p) = c_j(p)$ for \textbf{all} flow users.
\end{frame}

\begin{frame}{Sensitivity split}
	If $t_i \ne t_j$ then assume w.l.o.g. $t_i > t_j \Leftrightarrow \ell_i(x_i) < \ell_j(x_j)$.\\
	Low money-sensitive players will use link $i$.\\
	High money-sensitive players will use link $j$.

	\begin{table}[h!]
		\centering
		\caption{Summary of properties for the sensitivity split.}
		\begin{tabular}{| c || c | c |}
			\hline
			& \textbf{lower split} & \textbf{upper split} \\ \hline
			$\alpha$ & $\alpha(p) \le \as^{(i, j)}(t)$ & $\alpha(p) \ge \as^{(i, j)}(t)$ \\ \hline
			link & low-latency, high-toll & high-latency, low-toll \\ \hline
			sensitivity & time $\ge$ money & time $\le$ money \\ \hline
		\end{tabular}
		\label{table:split_summary}
	\end{table}
\end{frame}

\begin{frame}{Sensitivity split}
	\begin{definition}
		\label{definition:alpha_flow_sets}
		Let $(N, \ell, \alpha)$.
		We define as $A_i(t), A_i: \R_+^n \rightarrow \mathcal{P}(\R_+)$ the set of all possible $\alpha(p)$ values of players $p$ using link $i$ in $x(t)$.
		\[A_i(t) = \{\alpha(p) | f(p) = j \wedge t_j = t_i\}\]
	\end{definition}
\end{frame}

\begin{frame}{Sensitivity split}
	\begin{lemma}
		Let $(N, \ell, \alpha)$ and tolls $t$ where $t_i \ne t_j$ and $x_i(t), x_j(t) > 0$ for some links $i, j \in N$.
		Then:
		\begin{enumerate}[(i)]
			\item $\as^{(i, j)}(t) > 0$
			\item $\as^{(i, j)}(t) \in [\alpha(0), \alpha(1)]$
			%\item if $\as^{(i, j)}(t) < \alpha(0)$ (or $\as^{(i, j)}(t) > \alpha(1)$) then $x(t) = (0, 1)$ (or $(1, 0)$)
			\item if $\ell_i(x_i(t)) < \ell_j(x_j(t))$ then
			$\sup A_i(t) \le \as^{(i, j)}(t) \le \inf A_j(t)$
		\end{enumerate}
	\end{lemma}
\end{frame}

\begin{frame}{Sensitivity split | Monotonicity}
	\begin{lemma}
		Let $(N, \ell, \alpha)$ a heterogeneous parallel game and tolls $t, t^\prime$ such that for some links $i, j \in N$ it holds that $t_i \ne t_j, t_i^\prime \ne t_j^\prime$ and $t_k = t_k^\prime$ $\forall k \in N \setminus \{i, j\}$.
		If $x_i(t), x_j(t), x_i(t^\prime), x_j(t^\prime) > 0$ and $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} > 0$, then:
		\begin{enumerate}[(i)]
			\item if $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} \le 1$ then $\as^{(i, j)}(t) \ge \as^{(i, j)}(t^\prime)$
			\item if $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} \ge 1$ then $\as^{(i, j)}(t) \le \as^{(i, j)}(t^\prime)$
		\end{enumerate}
	\end{lemma}
\end{frame}

\begin{frame}{Sensitivity split | Monotonicity}
	\begin{proof}
		We prove $(i)$ and $(ii)$ follows symmetrically.\\
		If $x(t) = x(t^\prime)$ then the property follows from the definition of $\as$.
		If $x(t) \ne x(t^\prime)$ then assume w.l.o.g. that $x_i(t) > x_i(t^\prime)$, so a player $p$ moved from $i$ to $j$ between $t$ and $t^\prime$.
		\[\inf A_j(t^\prime) \le \alpha(p) \le \sup A_i(t)\]
		Applying the previous lemma gives us
		\[\as^{(i, j)}(t^\prime) \le \inf A_j(t^\prime) \le \sup A_i(t) \le \as^{(i, j)}(t)\]
	\end{proof}
\end{frame}

\begin{frame}{Sensitivity split | Limits}
	\begin{lemma}
		Let $(N, \ell, \alpha)$ a heterogeneous parallel game and tolls $t$ where $t_i \ne t_j$ and $x_i(t), x_j(t) > 0$ for some links $i, j \in N$.
		Then:
		\begin{enumerate}[(i)]
			\item
			\begin{flalign*}
				\lim_{|t_i - t_j| \rightarrow +\infty}\as^{(i, j)}(t) &= 0 &
			\end{flalign*}
			\item
			\begin{flalign*}
				\lim_{t_i - t_j \rightarrow 0^+} \as^{(i, j)}(t) &= \limsup_{t_i - t_j \rightarrow 0^+} A_i(t) &
			\end{flalign*}
		\end{enumerate}
	\end{lemma}
\end{frame}

\begin{frame}{Sensitivity split}
	\begin{figure}
		\centering
		\begin{tikzpicture}[x=2cm, y=2cm, every node/.style={font=\small}]
			% Axes
			\draw[->] (0,0) -- (-1.1,0);
			\draw[->] (0,0) -- (2.1,0) node[right] {$t_1 - t_2$};
			\draw[->] (0,0) -- (0,2.2) node[above] {$\as(t)$};

			% Tick marks
			\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
			\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
			\draw (2,0) -- (2,-0.05) node[below] {$2$};
			\draw (0,2) -- (-0.05, 2) node[left] {$2$};
			\draw (0,4/3) -- (0.05,4/3) node[right] {$4/3$};
			\draw (0,5/3) -- (-0.05,5/3) node[left] {$5/3$};
			\draw (0,1) -- (-0.05,1) node[left] {$1$};

			% Function graph
			%\draw[thick] (-1,1) -- (0,4/3);
			%\draw[thick] (0,5/3) -- (2,1);
			\draw[thick,domain=-1:0] plot (\x,{4/(3-\x)});
			\draw[thick,domain=0:2] plot (\x,{5/(3+\x)});

@@

	\begin{theorem}
		Let $\Gm_1 = (N, \ell, \alpha^{(1)})$ and $\Gm_2 = (N, \ell, \alpha^{(2)})$ be two heterogeneous parallel games and $x(0) = x^{(1)}(0) = x^{(2)}(0)$ the (equal) flow on paths for $t = 0$.
		If $\alpha^{(1)}$ and $\alpha^{(2)}$ are such that
		\[\alpha^{(1)}(p) = \alpha^{(2)}(p), \forall p: p < 1 - \min_{i \in N}\{x_i(0)\}\]
		then $\Gm_1$ and $\Gm_2$ are equivalent.
	\end{theorem}
\end{frame}

\begin{frame}{Sensitivity split | Upper bound}
	For the Example we have
	\[\max\{x_1(0), x_2(0)\} = \max\{2/3, 1/3\} = 2/3\]
	so if we used a distribution function such as
	\[
		\alpha(p) =
		\begin{cases}
			p + 1 & p \le 2/3 \\
			\mathrm{e}^p & p > 2/3
		\end{cases}
	\]
	then $\as(t)$ would remain the same for all $t \in \R_+^n$
\end{frame}

>>>>

\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level)}
	Tolls $t \in \R_+^n$ can be assigned to links, affecting player cost.

@@

		% Links
		\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
		\draw[->, thick] (s) to node[midway, above] {$x + 1$} (t);
		\draw[->, thick] (s) to[bend right=35] node[midway, above] {$x + 2$} (t);
	\end{tikzpicture}
\end{center}
For homogeneous players and tolls $t = (3, 2, 1)$
\[x(t) = \left(\frac15, \frac25, \frac25\right)\]
since $\ell_2(1/2) + t_2 = \ell_3(1/2) + t_3 = 7/2$ and $\ell_1(0) + t_1 = 4$.
\end{frame}

\begin{frame}{Preliminaries | Pricing competition (2\textsuperscript{nd} level)}
	Links are owned by agents who compete for profit.
	\begin{block}{Profit}
		For given set of tolls $t \in \R_+^n$, link operator $i$ gains profit
		\[\Pi_i(t) = x_i(t) \cdot t_i\]
	\end{block}
	\begin{block}{Best response}
		For fixed tolls assignments from remaining link operators $t_{-i} = t \setminus \{t_i\}$, link operator $i$ will try and maximise their profit
		\[B_i(t_{-i}) = \argmax_{t_i \ge 0} \Pi(t_i, t_{-i})\]
	\end{block}
\end{frame}

@@

@@

\begin{frame}{Sensitivity split | Heterogeneous networks}
	\begin{center}
		\begin{multicols}{2}
			% Left Column: Network Graph
			\begin{tikzpicture}[scale=1.2, baseline=40pt, every node/.style={font=\small}]
				% Nodes
				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};

				% Links
				\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
				\draw[->, thick] (s) to node[midway, above] {$x + 1$} (t);
				\draw[->, thick] (s) to[bend right=35] node[midway, above] {$x + 2$} (t);
			\end{tikzpicture}

			% Right Column: Distribution function Graph
			\begin{tikzpicture}[x=2.5cm, y=1.2cm, every node/.style={font=\small}]
				% Axes
				\draw[->] (0,0) -- (1.2,0) node[right] {$p$};
				\draw[->] (0,0) -- (0,2.2) node[above] {$\as(p)$};

				% Tick marks
				\draw (0,0) -- (0,-0.05) node[below] {$0$};
				\draw (1,0) -- (1,-0.05) node[below] {$1$};
				\draw (0,1) -- (-0.05,1) node[left] {$1$};
				\draw (0,2) -- (-0.05,2) node[left] {$2$};

				% Function graph
				\draw[thick] (0,1) -- (1,2);

				% Description
				\node[align=center] at (0.7, -0.8) {$\alpha(p) = p + 1$};
			\end{tikzpicture}
		\end{multicols}
	\end{center}
	For heterogeneous players with $\alpha(p) = p + 1$ and tolls $t = (3, 2, 1)$
	\[x(t) = \left(\frac{1}{11}, \frac{3}{11}, \frac{7}{11}\right)\]
\end{frame}

\tikzset{
	fixed_height/.style={
		inner sep=0,
		outer sep=0,
		minimum height=15pt,
		align=center
	}
}

\begin{frame}{Sensitivity split | Heterogeneous networks}
	Latencies are the same for all players.

	Toll ordering is the same for all players.

	Toll differences are viewed with different scaling.
	\\[15pt]
	\begin{tikzpicture}
		% Title
		\node[above,fixed_height] at (3.7,3.3) {$\alpha(0) = 1$};

		% Axes
		\draw[->] (0,0) -- (7,0) node[right=5,fixed_height] {$c\left(0\right)$};
		\draw[-] (0,0) -- (0,3.2);

		% Y-bars: Latencies
		\node[left] at (0,2.5) {$\frac{2}{11}$};
		\node[left] at (0,1.5) {$\frac{14}{11}$};
		\node[left] at (0,0.5) {$\frac{29}{11}$};
		\filldraw[fill=blue!20] (0,2.25) rectangle (2/11,2.75);
		\filldraw[fill=blue!20] (0,1.25) rectangle (14/11,1.75);
		\filldraw[fill=blue!20] (0,0.25) rectangle (29/11,0.75);

		% Y-bars: Tolls
		\filldraw[fill=orange!20] (2/11,2.25) rectangle (35/11,2.75) node[below right] {$3$};
		\filldraw[fill=orange!20] (14/11,1.25) rectangle (36/11,1.75) node[below right] {$2$};
		\filldraw[fill=orange!20] (29/11,0.25) rectangle (40/11,0.75) node[below right] {$1$};
	\end{tikzpicture}
\end{frame}

\begin{frame}{Sensitivity split | Heterogeneous networks}
	Latencies are the same for all players.

	Toll ordering is the same for all players.

	Toll differences are viewed with different scaling.
	\\[15pt]
	\begin{tikzpicture}
		% Title
		\node[above,fixed_height] at (3.7,3.3) {$\alpha\left(\frac{2}{11}\right) = \frac{13}{11}$};

		% Axes
		\draw[->] (0,0) -- (7,0) node[right=5,fixed_height] {$c\left(\frac{2}{11}\right)$};
		\draw[-] (0,0) -- (0,3.2);

		% Y-bars: Latencies
		\node[left] at (0,2.5) {$\frac{2}{11}$};
		\node[left] at (0,1.5) {$\frac{14}{11}$};
		\node[left] at (0,0.5) {$\frac{29}{11}$};
		\filldraw[fill=blue!20] (0,2.25) rectangle (2/11,2.75);
		\filldraw[fill=blue!20] (0,1.25) rectangle (14/11,1.75);
		\filldraw[fill=blue!20] (0,0.25) rectangle (29/11,0.75);

		% Y-bars: Tolls
		\filldraw[fill=orange!20] (2/11,2.25) rectangle (41/11,2.75) node[below right] {$\frac{39}{11}$};
		\filldraw[fill=orange!20] (14/11,1.25) rectangle (40/11,1.75) node[below right] {$\frac{26}{11}$};
		\filldraw[fill=orange!20] (29/11,0.25) rectangle (42/11,0.75) node[below right] {$\frac{13}{11}$};
	\end{tikzpicture}
\end{frame}

\begin{frame}{Sensitivity split | Heterogeneous networks}
	Latencies are the same for all players.

	Toll ordering is the same for all players.

	Toll differences are viewed with different scaling.
	\\[15pt]
	\begin{tikzpicture}
		% Title
		\node[above,fixed_height] at (3.7,3.3) {$\alpha(1) = 2$};

		% Axes
		\draw[->] (0,0) -- (7,0) node[right=5,fixed_height] {$c\left(1\right)$};
		\draw[-] (0,0) -- (0,3.2);

		% Y-bars: Latencies
		\node[left] at (0,2.5) {$\frac{2}{11}$};
		\node[left] at (0,1.5) {$\frac{14}{11}$};
		\node[left] at (0,0.5) {$\frac{29}{11}$};
		\filldraw[fill=blue!20] (0,2.25) rectangle (2/11,2.75);
		\filldraw[fill=blue!20] (0,1.25) rectangle (14/11,1.75);
		\filldraw[fill=blue!20] (0,0.25) rectangle (29/11,0.75);

		% Y-bars: Tolls
		\filldraw[fill=orange!20] (2/11,2.25) rectangle (64/11,2.75) node[below right] {$6$};
		\filldraw[fill=orange!20] (14/11,1.25) rectangle (58/11,1.75) node[below right] {$4$};
		\filldraw[fill=orange!20] (29/11,0.25) rectangle (51/11,0.75) node[below right] {$2$};
	\end{tikzpicture}
\end{frame}

\begin{frame}{Sensitivity split | Heterogeneous networks}
	Tolls define an ordering of the $N$ links where
	\begin{itemize}
		\item $t_1 \ge t_2 \ge \dots \ge t_n$
		\item $\ell_1(x_1(t)) \le \ell_2(x_2(t)) \le \dots \le \ell_n(x_n(t))$
		\item for player representatives from each link $p_1, p_2, \dots, p_n$ we also get $\alpha(p_1) \le \alpha(p_2) \le \dots \le \alpha(p_n)$
	\end{itemize}
	Ordering is unique only when the toll (and therefore also latency) inequalities are strict.
\end{frame}

\begin{frame}{Sensitivity split | Heterogeneous networks}
	For any pair of links $i, j$
	\begin{align*}
		c_i(&p) \le c_j(p) & c_i(p) \ge c_i(p&) \\[10pt]
		\alpha(p) \le &\frac{\ell_j(x_j) - \ell_i(x_i)}{t_i - t_j} & \frac{\ell_j(x_j) - \ell_i(x_i)}{t_i - t_j}& \le \alpha(p)
	\end{align*}
	We need the notion of the money-sensitivity value for which two link costs are equal.
\end{frame}

\begin{frame}{Sensitivity split}
	\begin{definition}
		Let $(N, \ell, \alpha)$, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$.
		We define the \textit{money sensitivity split function} for $i, j$ $\as^{(i, j)}: \{t \in \R_+^n|t_i \ne t_j\} \rightarrow (0, +\infty)$ as
		\[\as^{(i, j)}(t) = \frac{\ell_j(x_j(t)) - \ell_i(x_i(t))}{t_i - t_j}\]
	\end{definition}
	If $t_i = t_j \Leftrightarrow \ell_i(x_i) = \ell_j(x_j)$ then $c_i(p) = c_j(p)$ for \textbf{all} flow users.
\end{frame}

\begin{frame}{Sensitivity split}
	\begin{table}[h!]
		\centering
		\caption{Summary of properties for the sensitivity split.}
		\begin{tabular}{| c || c | c |}
			\hline
			& \textbf{lower split} & \textbf{upper split} \\ \hline
			$\alpha$ & $\alpha(p) \le \as^{(i, j)}(t)$ & $\alpha(p) \ge \as^{(i, j)}(t)$ \\ \hline
			link & low-latency, high-toll & high-latency, low-toll \\ \hline
			sensitivity & time $\ge$ money & time $\le$ money \\ \hline
		\end{tabular}
		\label{table:split_summary}
	\end{table}
\end{frame}

\begin{frame}{Sensitivity split}
	\begin{definition}
		Let $(N, \ell, \alpha)$.
		We define as $A_i(t), A_i: \R_+^n \rightarrow \mathcal{P}(\R_+)$ the set of all possible $\alpha(p)$ values of players $p$ using link $i$ in $x(t)$.
		\[A_i(t) = \{\alpha(p) | f(p) = j \wedge t_j = t_i\}\]
	\end{definition}
\end{frame}

\begin{frame}{Sensitivity split | Properties}
	\begin{lemma}
		Let $(N, \ell, \alpha)$ and tolls $t$ where for $i, j \in N$ $t_i \ne t_j$ and $x_i(t), x_j(t) > 0$.
		\begin{enumerate}[(i)]
			\item $\as^{(i, j)}(t) > 0$
			\item $\as^{(i, j)}(t) \in [\alpha(0), \alpha(1)]$
			\item if $\ell_i(x_i(t)) < \ell_j(x_j(t))$ then
			$\sup A_i(t) \le \as^{(i, j)}(t) \le \inf A_j(t)$
		\end{enumerate}
	\end{lemma}
\end{frame}

\begin{frame}{Sensitivity split | Properties}
	\begin{lemma}[Monotonicity]
		Let $t, t^\prime$ different only for $i, j \in N$ with the same toll ordering and $x_i(t), x_j(t), x_i(t^\prime), x_j(t^\prime) > 0$.
		Then
		\begin{enumerate}[(i)]
			\item if $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} \le 1$ then $\as^{(i, j)}(t) \ge \as^{(i, j)}(t^\prime)$
			\item if $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} \ge 1$ then $\as^{(i, j)}(t) \le \as^{(i, j)}(t^\prime)$
		\end{enumerate}
	\end{lemma}
\end{frame}

\begin{frame}{Sensitivity split | Properties}
	\begin{lemma}[Limit values]
		Let $(N, \ell, \alpha)$.
		Then:
		\begin{enumerate}[(i)]
			\item
			$\begin{aligned}[t]
				\lim_{|t_i - t_j| \rightarrow +\infty}\as^{(i, j)}(t) = 0
			\end{aligned}$
			\item
			$\begin{aligned}[t]
				\lim_{t_i - t_j \rightarrow 0^+} \as^{(i, j)}(t) = \limsup_{t_i - t_j \rightarrow 0^+} A_i(t)
			\end{aligned}$
		\end{enumerate}
	\end{lemma}
	\begin{corollary}
		$\begin{aligned}[t]
			\lim_{t_i - t_j \rightarrow 0^+} \as^{(i, j)}(t) = \alpha(x_i(0))
		\end{aligned}$
	\end{corollary}
\end{frame}

\begin{frame}{Sensitivity split | Properties}
	\begin{center}
		\begin{multicols}{2}
			% Left Column: Network Graph
			\begin{tikzpicture}[scale=1.2, baseline=40pt, every node/.style={font=\small}]
				% Nodes
				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};

			% Right Column: Distribution function Graph
			\begin{tikzpicture}[x=2.5cm, y=1.2cm, every node/.style={font=\small}]
				% Axes
				\draw[->] (0,0) -- (1.2,0) node[right] {$p$};
				\draw[->] (0,0) -- (0,2.2) node[above] {$\as(p)$};

				% Tick marks
				\draw (0,0) -- (0,-0.05) node[below] {$0$};
				\draw (1,0) -- (1,-0.05) node[below] {$1$};
				\draw (0,1) -- (-0.05,1) node[left] {$1$};
				\draw (0,2) -- (-0.05,2) node[left] {$2$};

				% Function graph
				\draw[thick] (0,1) -- (1,2);

				% Description
				\node[align=center] at (0.7, -0.8) {$\alpha(p) = p + 1$};
			\end{tikzpicture}
		\end{multicols}
	\end{center}
	\[x(0) = \left(\tfrac23, \tfrac13\right) \qquad \alpha(x_1(0)) = \tfrac53 \quad \alpha(x_2(0)) = \tfrac43\]
\end{frame}

\begin{frame}{Sensitivity split | Properties}
	\begin{figure}
		\centering
		\begin{tikzpicture}[x=2cm, y=2cm, every node/.style={font=\small}]
			% Axes
			\draw[->] (0,0) -- (-1.1,0);
			\draw[->] (0,0) -- (2.1,0) node[right] {$t_1 - t_2$};
			\draw[->] (0,0) -- (0,1.2) node[above] {$x_1(t)$};

			% Tick marks
			\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
			\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
			\draw (2,0) -- (2,-0.05) node[below] {$2$};
			\draw (0,1) -- (-0.05, 1) node[left] {$1$};

			% Function graph
			\draw[thick,domain=-1:0] plot (\x,{(2-2*\x)/(3-\x)});
			\draw[thick,domain=0:2] plot (\x,{(2-\x)/(3+\x)});

			% Dots
			\fill[black] (0,2/3) ellipse (0.03 and 0.03);
			\draw[black] (0,2/3) ellipse (0.03 and 0.03);
			\node[below left] at (0,2/3) {$\frac23$};
		\end{tikzpicture}
		\caption{Flow function of link operator $1$ of Example}
		\label{figure:alpha_simple:flow_example}
	\end{figure}
\end{frame}

\begin{frame}{Sensitivity split | Properties}
	\begin{figure}
		\centering
		\begin{tikzpicture}[x=2cm, y=2cm, every node/.style={font=\small}]
			% Axes
			\draw[->] (0,0) -- (-1.1,0);
			\draw[->] (0,0) -- (2.1,0) node[right] {$t_1 - t_2$};
			\draw[->] (0,0) -- (0,2.2) node[above] {$\as(t)$};

			% Tick marks
			\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
			\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
			\draw (2,0) -- (2,-0.05) node[below] {$2$};
			\draw (0,2) -- (-0.05, 2) node[left] {$2$};
			\draw (0,4/3) -- (0.05,4/3) node[right] {$\frac43$};
			\draw (0,5/3) -- (-0.05,5/3) node[left] {$\frac53$};
			\draw (0,1) -- (-0.05,1) node[left] {$1$};

			% Function graph
			\draw[thick,domain=-1:0] plot (\x,{4/(3-\x)});
			\draw[thick,domain=0:2] plot (\x,{5/(3+\x)});

@@

	\begin{theorem}
		Let $\Gm_1 = (N, \ell, \alpha^{(1)}), \Gm_2 = (N, \ell, \alpha^{(2)})$.\\
		For $x(0) = x^{(1)}(0) = x^{(2)}(0)$, if
		\[\alpha^{(1)}(p) = \alpha^{(2)}(p), \forall p: p < 1 - \min_{i \in N}\{x_i(0)\}\]
		then $\Gm_1$ and $\Gm_2$ are equivalent.
	\end{theorem}
\end{frame}

\begin{frame}{Sensitivity split | Upper bound}
	For the Example we have
	\[\max\{x_1(0), x_2(0)\} = \max\left\{\tfrac23, \tfrac13\right\} = \tfrac23\]
	so if we used a distribution function such as
	\[
		\alpha(p) =
		\begin{cases}
			p + 1 & p \le \tfrac23 \\
			\mathrm{e}^p & p > \tfrac23
		\end{cases}
	\]
	then $\as(t)$ would remain the same for all $t \in \R_+^n$
\end{frame}
